\documentclass[11pt]{article}
\usepackage{graphicx} % Required for inserting images
\setlength{\parindent}{0pt}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[utf8]{inputenc} 
\usepackage[T1]{fontenc}
\usepackage[brazil]{babel}
\usepackage{lipsum}
\usepackage[left=1.06cm,top=1.7cm,right=1.06cm,bottom=0.49cm]{geometry}




%by: Aline R. Antunes

\begin{document}
\begin{center}
    \textbf{Devarshi Maurya}\\ 
    \hrulefill
\end{center}

\begin{center}
    Ahmedabad, Gujarat \textbullet \ devarshimaurya0107@gmail.com \textbullet \  \url{https://github.com/Devarshi0107}\textbullet \ +91 9974121474
\end{center}

\vspace{0.5pt}

\begin{center}
    \textbf{Education}
\end{center}
\textbf{Charusat University} \hfill Changa, Gujarat

Degree, Concentration. CGPA : 9.0 [Till 3rd Sem] \hfill January, 2024

B.Tech in Information Technology

\vspace{12pt}

\textbf{Swami Vivekanand School} \hfill	Ahmedabad, Gujarat

Percentage : 76\%
\hfill June, 2022 

\vspace{12pt}

\begin{center}
    \textbf{Experience}
\end{center}
\textbf{Team Elementals} \hfill (Remote)

\textbf{Trainee Intern} \hfill May 2024 – August 2024
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
   \item Enhanced web development skills with CSS, HTML, and JavaScript.
    \item Acquired essential Linux knowledge for streamlined development.
    \item Developed proficiency in effective self-presentation through resume building.
    \item Gained valuable experience in teamwork dynamics through collaborative projects.
    \item Applied theoretical knowledge to solve real-life problems in practical scenarios.
\end{itemize}

\vspace{12pt}



\begin{center}
    \textbf{Leadership \& Activities}
\end{center}

\textbf{CP Squad Club , Charusat}	\hfill Changa, Gujarat

\textbf{Technical Cordinator} \hfill March 2024
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
   \item Organized and led technical workshops to foster skill development.
    \item Coordinated team efforts for coding competitions, ensuring effective collaboration.
    \item Provided guidance and support to club members, enhancing their learning experience.
    \item Facilitated communication among team members, promoting synergy and productivity.
    \item Implemented innovative solutions for technical challenges, driving progress and efficiency.

\end{itemize}


% trying
\vspace{12pt}



\begin{center}
    \textbf{Projects }
\end{center}

\textbf{Web Scholarship}	\hfill CVMU, Anand, Gujarat

\textbf{Hackathon Project} \hfill February 2024
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Created centralized scholarship web app for admin registration, approval, and management of scholarship details.
    \item Ensured secure authentication and validation processes for admin eligibility.
    \item Implemented user filters for efficient scholarship searching based on user profiles.
\end{itemize}

\vspace{12pt}

\textbf{Seat Reservation System for Restaurant}	\hfill CSPIT, Changa, Gujarat

\textbf{Software Group Project} \hfill 4th Sem
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Designed and developed a restaurant seat reservation system, enhancing user experience.
    \item Implemented a real-time table seat layout view for intuitive seat selection.
    \item Integrated functionality for efficient reservation processes, streamlining user interaction.

\end{itemize}

\vspace{12pt}

\begin{center}
    \textbf{Skills \& Interests }
\end{center}

\textbf{Technical:} C, C++, HTML, CSS, JS, React, Nodejs, Mongodb

\textbf{Language:} English (Intermediate), Hindi (Fluent),Gujarati (Fluent)

\textbf{Sports:} Enjoy casual games of chess and badminton.

\textbf{Interests:} Enthusiastic about action fiction movies, exploring new technologies, and learning about space exploration.




\end{document}
